Formalization of Abstract Rewriting

### 2025-11-03 Relations/Paper/Main.tex
remove todo from main
Todos started and simple fixes made.
section 2
Updated bibliography
Changes from last meeting and minor edits.
Finished section 5

% \usepackage[dvipsnames]{xcolor}

@@

\keywords{Abstract rewriting, Formalization, Confluence, Strong normalization, Newman's Lemma} %TODO mandatory; please add comma-separated list of keywords

\supplement{https://github.com/DrPolonsky/LAM//tree/main/ARS}% TODO: set a repo just for this submissionoptional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

\begin{document}
\maketitle

\begin{abstract}
    We present a constructive formalization of Abstract Reduction Systems (ARS)
     in the Agda proof assistant, focusing on the results given in
     the standard reference on Term Rewriting Systems \cite{Terese}. We define a taxonomy of concepts related to termination and
     confluence and investigate their relationships between each other and their
     classical counterparts. We identify, and eliminate where possible, the use of classical
     logic in the proofs of standard ARS results. Our analysis leads to refinements and mild
      generalizations of classical termination and confluence criteria.
\end{abstract}

\input{Introduction.tex}
\input{Definitions.tex}
\input{Formalization.tex}
\input{Implications.tex}
\input{Well-foundedness.tex}
\input{Conclusion.tex}
\input{FinalTODO.tex}

@@

    \bibitem{mimram}
    Mimram, Samuel
    \newblock{Program= Proof}.
    \newblock{2020}.

    \bibitem{Berardi}
    Marc Bezem, Thierry Coquand, Keiko Nakata, and Erik Parmann.
    \newblock{Realizability at Work: Separating Two Constructive Notions of Finiteness}.
    \newblock {In 22nd International Conference on Types for Proofs and Programs (TYPES 2016)}.
    \newblock{Leibniz International Proceedings in Informatics (LIPIcs), Volume 97, pp. 6:1-6:23, Schloss Dagstuhl – Leibniz-Zentrum für Informatik (2018)}.
    \newblock{https://doi.org/10.4230/LIPIcs.TYPES.2016.6}.

    \bibitem{Bezem}
    Stefano Berardi 
    \newblock{Classical and Intuitionistic Arithmetic with Higher Order Comprehension Coincide on Inductive Well-Foundedness}.
    \newblock{In 24th EACSL Annual Conference on Computer Science Logic (CSL 2015) }.
    \newblock{Leibniz International Proceedings in Informatics (LIPIcs), Volume 41, pp. 343-358}.
     \newblock{Schloss Dagstuhl – Leibniz-Zentrum für Informatik (2015)}.
      \newblock{https://doi.org/10.4230/LIPIcs.CSL.2015.343}.

>>>>

% \usepackage[dvipsnames]{xcolor}
\newtheorem{notation}[theorem]{Notation}

@@

\keywords{Abstract rewriting, Formalization, Confluence, Strong normalization, Newman's Lemma, Well-foundedness} %TODO mandatory; please add comma-separated list of keywords

\supplement{https://github.com/DrPolonsky/FPLA/tree/main}

\renewcommand\eminnershape{\bfseries}
\begin{document}
\maketitle

\begin{abstract}
    We present a constructive formalization of Abstract Reduction Systems (ARS)
     in the Agda proof assistant, focusing on the results given in
     the standard reference on Term Rewriting Systems \cite{Terese}. We define a taxonomy of concepts related to termination and
     confluence and investigate their relationships between each other and their
     classical counterparts. We identify, and eliminate where possible, the use of classical
     logic in the proofs of standard ARS results. Our analysis leads to refinements and mild
      generalizations of classical termination and confluence criteria.
      Finally, we investigate logical relationships between several notions of termination, 
      arising from different formulations of the concept of a well-founded relation.
    \end{abstract}

\input{Introduction.tex}
\input{Definitions.tex}
\input{Formalization.tex}
\input{Implications.tex}
\input{Well-foundedness.tex}
\input{Conclusion.tex}
% \input{FinalTODO.tex}

@@

    \bibitem{mimram}
    Mimram, Samuel
    \newblock{Program= Proof}.
    \newblock{2020}.
    \newblock{isbn = 9798615591839}.
    \newblock{Independently Published}.

    \bibitem{Bezem}
    Marc Bezem, Thierry Coquand, Keiko Nakata, and Erik Parmann.
    \newblock{Realizability at Work: Separating Two Constructive Notions of Finiteness}.
    \newblock {In 22nd International Conference on Types for Proofs and Programs (TYPES 2016)}.
    \newblock{Leibniz International Proceedings in Informatics (LIPIcs), Volume 97, pp. 6:1-6:23, Schloss Dagstuhl – Leibniz-Zentrum für Informatik (2018)}.
    \newblock{https://doi.org/10.4230/LIPIcs.TYPES.2016.6}.

    \bibitem{Berardi}
    Stefano Berardi
    \newblock{Classical and Intuitionistic Arithmetic with Higher Order Comprehension Coincide on Inductive Well-Foundedness}.
    \newblock{In 24th EACSL Annual Conference on Computer Science Logic (CSL 2015) }.
    \newblock{Leibniz International Proceedings in Informatics (LIPIcs), Volume 41, pp. 343-358}.
     \newblock{Schloss Dagstuhl – Leibniz-Zentrum für Informatik (2015)}.
      \newblock{https://doi.org/10.4230/LIPIcs.CSL.2015.343}.

    \bibitem{AgdaLibraryList}
    Agda Standard Library: List 
    \newblock{https://agda.github.io/agda-stdlib/v2.2/Agda.Builtin.List.html}
    \newblock{Accessed: 8th July 2025}
